03_limma_pit

### 2019-04-03 analysis/02_limma_hyp.Rmd
moved printplotcontrasts function

```{r}
library(tidyverse)
library(limma)
library(Glimma)
library(edgeR)
library(kableExtra)
library(cowplot)
library(ggplot2)

@@

mycontrasts <- c("FH_CB", "FH_BL", "FH_Li3", "FH_i39", "FH_i917", "FH_i17H", "FH_H5", "FH_n59", "FH_n9C",
                 "MH_CB", "MH_BL", "MH_Li3", "MH_i39", "MH_i917", "MH_i17H", "MH_H5", "MH_n59", "MH_n9C",
                 "FH_n9B", "MH_n9B")

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  print(summary(decideTestsDGE(
    glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
    adjust.method="fdr", p.value=0.01)))
  print(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
  print(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}

for(i in mycontrasts){
  printplotcontrasts(i)
}

>>>>

```{r}
library(tidyverse)
library(limma)
library(Glimma)
library(edgeR)
library(kableExtra)
library(cowplot)

# load custom functions
source("../R/functions.R")

@@

# create a list with all the two way contrasts
mycontrasts <- c("FH_CB", "FH_BL", "FH_Li3", "FH_i39", "FH_i917", "FH_i17H", "FH_H5", "FH_n59", "FH_n9C",
                 "MH_CB", "MH_BL", "MH_Li3", "MH_i39", "MH_i917", "MH_i17H", "MH_H5", "MH_n59", "MH_n9C",
                 "FH_n9B", "MH_n9B")

# use the printplotcontrasts function to print summary stats and a volcano plot

for(i in mycontrasts){
  printplotcontrasts(i)
}
```

### 2019-04-03 analysis/03_limma_pit.Rmd
moved printplotcontrasts function

@@

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  print(summary(decideTestsDGE(
    glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
    adjust.method="fdr", p.value=0.01)))
  print(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
  print(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}

>>>>

# create a list with all the two way contrasts

@@

# use the printplotcontrasts function to print summary stats and a volcano plot
